Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-16 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Replace biimp by equiv in definitions

\begin{definition}
\label{D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{definition}
\label{D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties:
$$
\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

@@

\begin{definition}
\label{D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{definition}
\label{N:D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{definition}
\label{N:D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties:
$$
\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

@@

\begin{definition}
\label{N:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{definition}[Emended]
\label{A:D1}
A \emph{God-like} being necessarily possesses those and only those properties which are positive:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \biimp \nec \varphi(x)]
$$
\end{definition}

@@

\begin{definition}[Emended]
\label{A:D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying those and only those properties necessarily possessed by it:
$$
\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\nec \psi(x) \biimp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

\begin{definition}[As in Scott's]
\label{A:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

>>>>

\begin{definition}
\label{D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{definition}
\label{D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties:
$$
\ess{\varphi}{x} \equiv \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

@@

\begin{definition}
\label{D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{definition}
\label{N:D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{definition}
\label{N:D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties:
$$
\ess{\varphi}{x} \equiv \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

@@

\begin{definition}
\label{N:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{definition}[Emended]
\label{A:D1}
A \emph{God-like} being necessarily possesses those and only those properties which are positive:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \biimp \nec \varphi(x)]
$$
\end{definition}

@@

\begin{definition}[Emended]
\label{A:D2}
An \emph{essence} of an individual is a property possessed by it and necessarily implying those and only those properties necessarily possessed by it:
$$
\ess{\varphi}{x} \equiv \varphi(x) \wedge \all \psi. (\nec \psi(x) \biimp \nec \all x. (\varphi(x) \imp \psi(x)))
$$
\end{definition}

\begin{definition}[As in Scott's]
\label{A:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}
